\pkg{casebase}: An Alternative Framework For Survival Analysis

### 2020-07-18 analysis/paper/paper.tex
fixed comparison table. and consistent themes or figures

Parametric survival models are implemented in a handful of packages:
\pkg{CFC} \citeyearpar{mahani2015bayesian}, \pkg{flexsurv}
\citeyearpar{flexsurv}, \pkg{SmoothHazard} \citeyearpar{smoothHazard},
\pkg{rsptm2} \citeyearpar{clements_liu}, \pkg{mets}
\citeyearpar{scheike2014estimating}, and \pkg{survival}
\citeyearpar{survival-package}. The types of models they allow vary for
each package. For example, \pkg{SmoothHazard} is limited to Weibull
distributions \citeyearpar{smoothHazard}, whereas both \pkg{flexsurv}
and \pkg{survival} allow users to supply any distribution of their
choice. Also, \pkg{flexsurv}, \pkg{smoothhazard}, \pkg{mets} and
\pkg{rstpm2} also have the ability to model the effect of time using
splines, which allows flexible modeling of the hazard function.
Moreover, \pkg{flexsurv} has the ability to estimate both scale and
shape parameters for a variety of parametric families (see Table
\ref{tab:dists}). As discussed above, \pkg{casebase} can model any
parametric family whose log-hazard can be expressed as a linear
combination of covariates (including time). Therefore, our package
allows the user to model the effect of time using splines. Also, by
including interaction terms between covariates and time, it also allows
users to fit time-varying coefficient models. However, we do not
explicitly model any shape parameter, unlike \pkg{flexsurv}.

@@

\begin{center}\includegraphics{../figures/plot-stratified-erspc-data-1} \end{center}

@@

@@

\begin{CodeOutput}
#> Analysis of Deviance Table
#> 
#> Model 1: DeadOfPrCa ~ ScrArm + offset(offset)
#> Model 2: DeadOfPrCa ~ bs(Follow.Up.Time) + ScrArm + offset(offset)
#>   Resid. Df Resid. Dev Df Deviance            Pr(>Chi)    
#> 1     54538       6053                                    
#> 2     54535       5788  3      265 <0.0000000000000002 ***
#> ---
#> Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#>    Exp.   Gomp.   Weib. Splines 
#>    6057    5818    6057    5798
\end{CodeOutput}
\end{CodeChunk}

@@

\caption{\label{tab:print-erspc-estimates}Comparison of estimated hazard ratios and 95\% confidence intervals for ERSPC data.}
\centering
\begin{tabular}[t]{>{\bfseries}lcc}
\toprule
Model & casebase::fitSmoothHazard & survival::survreg\\
\midrule
Exponential & 0.81 (0.68, 0.96) & 0.81 (0.68, 0.96)\\
\cmidrule{1-3}
Gompertz & 0.79 (0.66, 0.94) & 0.80 (0.67, 0.95)\\
\cmidrule{1-3}
Weibull & 0.81 (0.68, 0.97) & 0.80 (0.65, 0.96)\\
\cmidrule{1-3}
Splines & 0.80 (0.67, 0.95) & --\\
\bottomrule
\multicolumn{3}{l}{Cox model estimate: HR (95\% CI) = 0.80 (0.67, 0.95)}\\
\end{tabular}
\end{table}

@@

@@

@@

\begin{CodeInput}
R> library(survival)
R> # Treat competing event as censoring
R> model_cox <- coxph(Surv(ftime, Status == 1) ~ Sex + D + Phase + Source + Age,
R>   data = bmtcrr
R> )
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeInput}
R> library(timereg)
R> model_fg <- comp.risk(Event(ftime, Status) ~ const(Sex) + const(D) +
R>                         const(Phase) + const(Source) + const(Age),
R>                       data = bmtcrr, cause = 1, model = "fg")
R> 
R> # Estimate absolute risk curve
R> risk_fg <- predict(model_fg, newdata, times = time_points)
\end{CodeInput}
\end{CodeChunk}

@@

@@

\begin{CodeInput}
R> x <- model.matrix(death ~ . - d.time - aps - sps, 
R>                   data = train)[, -c(1)] # Remove intercept
R> y <- data.matrix(subset(train, select = c(d.time, death)))
R> 
R> # Regularized logistic regression to estimate hazard
R> cbFull <- casebase::fitSmoothHazard.fit(x, y,
R>   family = "glmnet",
R>   time = "d.time", event = "death",
R>   formula_time = ~ log(d.time), alpha = 1,
R>   ratio = 10, standardize = TRUE,
R>   penalty.factor = c(0, rep(1, ncol(x)))
R> )
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeInput}
R> # Estimating the absolute risk curve using the newdata parameter
R> newx <- model.matrix(death ~ . - d.time - aps - sps, 
R>                   data = test)[, -c(1)]
R> times <- sort(unique(test$d.time))
R> 
R> abCbFull <- casebase::absoluteRisk(cbFull,
R>   time = times,
R>   newdata = newx,
R>   s = "lambda.1se",
R>   method = "numerical"
R> )
\end{CodeInput}
\end{CodeChunk}

@@

@@

@@

@@

@@

\begin{CodeInput}
R> # Compute hazards---
R> # First, create a list of time points for both exposure status
R> hazard_data <- expand.grid(
R>   exposure = c(0, 1),
R>   futime = seq(0, 1000,
R>     length.out = 100
R>   )
R> )
R> # Set the offset to zero
R> hazard_data$offset <- 0
R> # Use predict to get the fitted values, and exponentiate to
R> # transform to the right scale
R> hazard_data$hazard <- exp(predict(fit4,
R>   newdata = hazard_data,
R>   type = "link"
R> ))
R> # Add labels for plots
R> hazard_data$Status <- factor(hazard_data$exposure,
R>   labels = c("NoTrans", "Trans")
R> )
R> 
R> ggplot(hazard_data, aes(futime, hazard, colour = Status)) +
R>   geom_line() +
R>   theme_minimal() +
R>   theme(legend.position = "top") +
R>   ylab("Hazard") +
R>   xlab("Follow-up time")
\end{CodeInput}
\end{CodeChunk}

@@

@@

@@

@@

@@

This report was generated on 2020-07-18 13:50:44 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> R version 3.6.2 (2019-12-12)
#> Platform: x86_64-pc-linux-gnu (64-bit)
#> Running under: Pop!_OS 19.10
#> 
#> Matrix products: default
#> BLAS:   /usr/lib/x86_64-linux-gnu/openblas/libblas.so.3
#> LAPACK: /usr/lib/x86_64-linux-gnu/libopenblasp-r0.3.7.so
#> 
#> locale:
#>  [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C              
#>  [3] LC_TIME=en_US.UTF-8        LC_COLLATE=en_US.UTF-8    
#>  [5] LC_MONETARY=en_US.UTF-8    LC_MESSAGES=en_US.UTF-8   
#>  [7] LC_PAPER=en_US.UTF-8       LC_NAME=C                 
#>  [9] LC_ADDRESS=C               LC_TELEPHONE=C            
#> [11] LC_MEASUREMENT=en_US.UTF-8 LC_IDENTIFICATION=C       
#> 
#> attached base packages:
#> [1] splines   stats     graphics  grDevices utils     datasets  methods  
#> [8] base     
#> 
#> other attached packages:
#>  [1] forcats_0.5.0             stringr_1.4.0            
#>  [3] dplyr_0.8.5               purrr_0.3.4              
#>  [5] readr_1.3.1               tidyr_1.1.0              
#>  [7] ggplot2_3.3.2.9000        tidyverse_1.3.0          
#>  [9] lubridate_1.7.4           visreg_2.7.0             
#> [11] tibble_3.0.1              riskRegression_2020.02.05
#> [13] prodlim_2019.11.13        flexsurv_1.1.1           
#> [15] survival_3.1-8            pracma_2.2.9             
#> [17] magrittr_1.5              kableExtra_1.1.0         
#> [19] glmnet_4.0-2              Matrix_1.2-18            
#> [21] data.table_1.12.8         cowplot_1.0.0            
#> [23] colorspace_1.4-1          casebase_0.9.0           
#> 
#> loaded via a namespace (and not attached):
#>  [1] TH.data_1.0-10      VGAM_1.1-3          ellipsis_0.3.1     
#>  [4] htmlTable_1.13.3    base64enc_0.1-3     fs_1.3.2           
#>  [7] rstudioapi_0.11     farver_2.0.3        MatrixModels_0.4-1 
#> [10] fansi_0.4.1         mvtnorm_1.0-12      xml2_1.3.0         
#> [13] codetools_0.2-16    knitr_1.29          Formula_1.2-3      
#> [16] jsonlite_1.7.0      broom_0.7.0         cluster_2.1.0      
#> [19] dbplyr_1.4.2        png_0.1-7           compiler_3.6.2     
#> [22] httr_1.4.1          backports_1.1.8     assertthat_0.2.1   
#> [25] cli_2.0.2           acepack_1.4.1       htmltools_0.5.0    
#> [28] quantreg_5.54       tools_3.6.2         gtable_0.3.0       
#> [31] glue_1.4.1          Rcpp_1.0.4.6        cellranger_1.1.0   
#> [34] vctrs_0.3.1         nlme_3.1-143        iterators_1.0.12   
#> [37] xfun_0.15           rvest_0.3.5         lifecycle_0.2.0    
#> [40] polspline_1.1.17    muhaz_1.2.6.1       MASS_7.3-51.5      
#> [43] zoo_1.8-7           scales_1.1.1        hms_0.5.3          
#> [46] sandwich_2.5-1      SparseM_1.78        RColorBrewer_1.1-2 
#> [49] rticles_0.13        yaml_2.2.1          gridExtra_2.3      
#> [52] rms_5.1-4           rpart_4.1-15        latticeExtra_0.6-29
#> [55] stringi_1.4.6       foreach_1.5.0       checkmate_2.0.0    
#> [58] lava_1.6.6          shape_1.4.4         rlang_0.4.6        
#> [61] pkgconfig_2.0.3     evaluate_0.14       lattice_0.20-38    
#> [64] labeling_0.3        htmlwidgets_1.5.1   cmprsk_2.2-9       
#> [67] tidyselect_1.1.0    deSolve_1.27.1      R6_2.4.1           
#> [70] generics_0.0.2      Hmisc_4.3-1         multcomp_1.4-12    
#> [73] DBI_1.1.0           withr_2.2.0         pillar_1.4.4       
#> [76] haven_2.3.1         foreign_0.8-74      mgcv_1.8-31        
#> [79] nnet_7.3-12         mstate_0.2.12       modelr_0.1.5       
#> [82] crayon_1.3.4        rmarkdown_2.3       timereg_1.9.4      
#> [85] jpeg_0.1-8.1        grid_3.6.2          readxl_1.3.1       
#> [88] reprex_0.3.0        digest_0.6.25       webshot_0.5.2      
#> [91] numDeriv_2016.8-1.1 stats4_3.6.2        munsell_0.5.0      
#> [94] viridisLite_0.3.0   quadprog_1.5-8
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> Local:    write-popTime /home/sahir/git_repositories/cbpaper
#> Remote:   write-popTime @ origin (https://github.com/sahirbhatnagar/cbpaper.git)
#> Head:     [84d5ff5] 2020-06-29: merge pop-stash
\end{CodeOutput}
\end{CodeChunk}

>>>>

Parametric survival models are implemented in a handful of packages:
\pkg{CFC} \citeyearpar{mahani2015bayesian}, \pkg{flexsurv}
\citeyearpar{flexsurv}, \pkg{SmoothHazard} \citeyearpar{smoothHazard},
\pkg{rsptm2} \citeyearpar{clements_liu}, \pkg{mets}
\citeyearpar{scheike2014estimating}, and \pkg{survival}
\citeyearpar{survival-package}. The types of models they allow vary for
each package. For example, \pkg{SmoothHazard} is limited to Weibull
distributions \citeyearpar{smoothHazard}, whereas both \pkg{flexsurv}
and \pkg{survival} allow users to supply any distribution of their
choice. Also, \pkg{flexsurv}, \pkg{smoothhazard}, \pkg{mets} and
\pkg{rstpm2} also have the ability to model the effect of time using
splines, which allows flexible modeling of the hazard function.
Moreover, \pkg{flexsurv} has the ability to estimate both scale and
shape parameters for a variety of parametric families. As discussed
above, \pkg{casebase} can model any parametric family whose log-hazard
can be expressed as a linear combination of covariates (including time).
Therefore, our package allows the user to model the effect of time using
splines. Also, by including interaction terms between covariates and
time, it also allows users to fit time-varying coefficient models.
However, we do not explicitly model any shape parameter, unlike
\pkg{flexsurv}.

@@

{\centering \includegraphics{../figures/plot-stratified-erspc-data-1}

\caption[Population time plot for ERSPC data]{Population time plot for ERSPC data.}\label{fig:plot-stratified-erspc-data}
\end{figure}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> 
#> Call:
#> glm(formula = formula, family = binomial, data = sampleData)
#> 
#> Deviance Residuals: 
#>    Min      1Q  Median      3Q     Max  
#> -0.378  -0.162  -0.122  -0.094   3.468  
#> 
#> Coefficients:
#>                       Estimate Std. Error z value            Pr(>|z|)    
#> (Intercept)            -9.0335     0.1122  -80.54 <0.0000000000000002 ***
#> Follow.Up.Time          0.2228     0.0145   15.32 <0.0000000000000002 ***
#> ScrArmScreening group  -0.2340     0.0886   -2.64              0.0083 ** 
#> ---
#> Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
#> 
#> (Dispersion parameter for binomial family taken to be 1)
#> 
#>     Null deviance: 6059.0  on 54539  degrees of freedom
#> Residual deviance: 5810.1  on 54537  degrees of freedom
#> AIC: 5816
#> 
#> Number of Fisher Scoring iterations: 8
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> Analysis of Deviance Table
#> 
#> Model 1: DeadOfPrCa ~ ScrArm + offset(offset)
#> Model 2: DeadOfPrCa ~ bs(Follow.Up.Time) + ScrArm + offset(offset)
#>   Resid. Df Resid. Dev Df Deviance            Pr(>Chi)    
#> 1     54538       6053                                    
#> 2     54535       5787  3      266 <0.0000000000000002 ***
#> ---
#> Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#>    Exp.   Gomp.   Weib. Splines 
#>    6057    5816    6057    5797
\end{CodeOutput}
\end{CodeChunk}

@@

\caption{\label{tab:print-erspc-estimates}Comparison of estimated hazard ratios and 95\% confidence intervals for ERSPC data.}
\centering
\begin{tabular}[t]{>{\bfseries}lcc}
\toprule
Model & casebase::fitSmoothHazard & survival::survreg\\
\midrule
Exponential & 0.81 (0.68, 0.96) & 0.81 (0.68, 0.96)\\
\cmidrule{1-3}
Gompertz & 0.79 (0.66, 0.94) & 0.80 (0.67, 0.95)\\
\cmidrule{1-3}
Weibull & 0.81 (0.68, 0.96) & 0.80 (0.65, 0.96)\\
\cmidrule{1-3}
Splines & 0.81 (0.68, 0.96) & --\\
\bottomrule
\multicolumn{3}{l}{Cox model estimate: HR (95\% CI) = 0.80 (0.67, 0.95)}\\
\end{tabular}
\end{table}

@@

\caption{\label{tab:table1bmtcrr}Baseline characteristics of patients in the stem-cell transplant study.}
\centering
\begin{tabular}[t]{lll}
\toprule
Variable & Description & Statistical summary\\
\midrule
\code{Sex} & Sex & M=Male (100)\\
 &  & F=Female (77)\\
\code{D} & Disease & ALL (73)\\
 &  & AML (104)\\
\code{Phase} & Phase & CR1 (47)\\
\addlinespace
 &  & CR2 (45)\\
 &  & CR3 (12)\\
 &  & Relapse (73)\\
\code{Source} & Type of transplant & BM+PB (21)\\
 &  & PB (156)\\
\addlinespace
\code{Age} & Age of patient (years) & 4--62\\
 &  & 30.47 (13.04)\\
\code{ftime} & Failure time (months) & 0.13--131.77\\
 &  & 20.28 (30.78)\\
\code{Status} & Status indicator & 0=censored (46)\\
\addlinespace
 &  & 1=relapse (56)\\
 &  & 2=competing event (75)\\
\bottomrule
\end{tabular}
\end{table}

@@

{\centering \includegraphics{../figures/compPop-1}

\caption[Population-time plot for the stem-cell transplant study with both relapse and competing events]{Population-time plot for the stem-cell transplant study with both relapse and competing events.}\label{fig:compPop}
\end{figure}
\end{CodeChunk}

@@

\begin{CodeInput}
R> library(survival)
R> # Treat competing event as censoring
R> model_cox <- coxph(Surv(ftime, Status == 1) ~ Sex + D + Phase + Source + Age,
R+   data = bmtcrr
R+ )
\end{CodeInput}
\end{CodeChunk}

\caption{\label{tab:bmtcrr-cis}Estimates and confidence intervals for the hazard ratios for each coefficient. Both estimates from case-base sampling and Cox regression are presented.}
\centering
\begin{tabular}[t]{lrlrl}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Case-Base} & \multicolumn{2}{c}{Cox} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
Covariates & HR & 95\% CI & HR & 95\% CI\\
\midrule
Sex & 0.70 & (0.4, 1.23) & 0.68 & (0.39, 1.19)\\
Disease & 0.53 & (0.29, 0.95) & 0.52 & (0.29, 0.93)\\
Phase (CR2 vs. CR1) & 1.12 & (0.45, 2.78) & 1.21 & (0.48, 3.02)\\
Phase (CR3 vs. CR1) & 1.45 & (0.37, 5.66) & 1.67 & (0.43, 6.5)\\
Phase (Relapse vs. CR1) & 4.04 & (1.88, 8.68) & 4.55 & (2.09, 9.9)\\
\addlinespace
Source & 1.48 & (0.48, 4.54) & 1.46 & (0.47, 4.54)\\
Age & 0.99 & (0.97, 1.01) & 0.99 & (0.97, 1.02)\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{CodeInput}
R> library(timereg)
R> model_fg <- comp.risk(Event(ftime, Status) ~ const(Sex) + const(D) +
R+                         const(Phase) + const(Source) + const(Age),
R+                       data = bmtcrr, cause = 1, model = "fg")
R> 
R> # Estimate absolute risk curve
R> risk_fg <- predict(model_fg, newdata, times = time_points)
\end{CodeInput}
\end{CodeChunk}

{\centering \includegraphics{../figures/bmtcrr-risk-1}

\caption{\label{fig:compAbsrisk} Absolute risk curve for a fixed covariate profile and the two disease groups. The estimate obtained from case-base sampling is compared to the Kaplan-Meier estimate.}\label{fig:bmtcrr-risk}
\end{figure}
\end{CodeChunk}

@@

{\centering \includegraphics{../figures/brierpt1-1}

\caption{\label{fig:brier1} Comparison of three Cox regression models. (A) Cumulative Incidence curves. (B) Time-dependent Brier scores.}\label{fig:brierpt1}
\end{figure}
\end{CodeChunk}

@@

\begin{CodeInput}
R> x <- model.matrix(death ~ . - d.time - aps - sps, 
R+                   data = train)[, -c(1)] # Remove intercept
R> y <- data.matrix(subset(train, select = c(d.time, death)))
R> 
R> # Regularized logistic regression to estimate hazard
R> cbFull <- casebase::fitSmoothHazard.fit(x, y,
R+   family = "glmnet",
R+   time = "d.time", event = "death",
R+   formula_time = ~ log(d.time), alpha = 1,
R+   ratio = 10, standardize = TRUE,
R+   penalty.factor = c(0, rep(1, ncol(x)))
R+ )
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeInput}
R> # Estimating the absolute risk curve using the newdata parameter
R> newx <- model.matrix(death ~ . - d.time - aps - sps, 
R+                   data = test)[, -c(1)]
R> times <- sort(unique(test$d.time))
R> 
R> abCbFull <- casebase::absoluteRisk(cbFull,
R+   time = times,
R+   newdata = newx,
R+   s = "lambda.1se",
R+   method = "numerical"
R+ )
\end{CodeInput}
\end{CodeChunk}

@@

{\centering \includegraphics{../figures/coefplots-1}

\caption{\label{fig:cs3lolliPlot} Lollipop plot showing the coefficient estimates between three models. If a coefficient estimate is 0 in any model, it is removed from the plot for simplicity.}\label{fig:coefplots}
\end{figure}
\end{CodeChunk}

@@

{\centering \includegraphics{../figures/riskregressionBrier-1}

\caption{\label{fig:cs3FinalBrier} Four curves comparing the Cumulative Incidence (A) and the Brier scores (B) as they change over time between Cox regression, penalized Cox regression, penalized logistic regression, and Kaplan-Meier.}\label{fig:riskregressionBrier}
\end{figure}
\end{CodeChunk}

@@

\begin{center}\includegraphics{../figures/stanford-poptime-1} \end{center}

@@

\begin{CodeOutput}
#> Model1 Model2 Model3 Model4 
#>    845    491    495    486
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeInput}
R> # Compute hazards---
R> # First, create a list of time points for both exposure status
R> hazard_data <- expand.grid(
R>   exposure = c(0, 1),
R>   futime = seq(0, 1000,
R>     length.out = 100
R>   )
R> )
R> 
R> # Set the offset to zero
R> hazard_data$offset <- 0
R> # Use predict to get the fitted values, and exponentiate to
R> # transform to the right scale
R> hazard_data$hazard <- exp(predict(fit4,
R>   newdata = hazard_data,
R>   type = "link"
R> ))
R> # Add labels for plots
R> hazard_data$Status <- factor(hazard_data$exposure,
R>   labels = c("NoTrans", "Trans")
R> )
R> 
R> ggplot(hazard_data, aes(futime, hazard, colour = Status)) +
R>   geom_line() +
R>   theme_minimal() +
R>   theme(legend.position = "top") +
R>   ylab("Hazard") +
R>   xlab("Follow-up time")
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> [1] "absRiskCB" "matrix"
\end{CodeOutput}

\begin{center}\includegraphics{../figures/stanford-risk-1} \end{center}

@@

\begin{center}\includegraphics{../figures/stanford-1y-haz-1} \end{center}

@@

\begin{CodeOutput}
#>  time  
#>     0 0
#>   365 1
\end{CodeOutput}

\begin{CodeOutput}
#> [1] 0.99
\end{CodeOutput}
\end{CodeChunk}

@@

We can also plot the Hazard ratio:

\begin{center}\includegraphics{../figures/unnamed-chunk-12-1} \end{center}

@@

This report was generated on 2020-07-18 15:04:50 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> R version 3.6.2 (2019-12-12)
#> Platform: x86_64-pc-linux-gnu (64-bit)
#> Running under: Pop!_OS 19.10
#> 
#> Matrix products: default
#> BLAS:   /usr/lib/x86_64-linux-gnu/openblas/libblas.so.3
#> LAPACK: /usr/lib/x86_64-linux-gnu/libopenblasp-r0.3.7.so
#> 
#> locale:
#>  [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C              
#>  [3] LC_TIME=en_US.UTF-8        LC_COLLATE=en_US.UTF-8    
#>  [5] LC_MONETARY=en_US.UTF-8    LC_MESSAGES=en_US.UTF-8   
#>  [7] LC_PAPER=en_US.UTF-8       LC_NAME=C                 
#>  [9] LC_ADDRESS=C               LC_TELEPHONE=C            
#> [11] LC_MEASUREMENT=en_US.UTF-8 LC_IDENTIFICATION=C       
#> 
#> attached base packages:
#> [1] splines   stats     graphics  grDevices utils     datasets  methods  
#> [8] base     
#> 
#> other attached packages:
#>  [1] broom_0.7.0               dotwhisker_0.5.0         
#>  [3] timereg_1.9.4             glue_1.4.1               
#>  [5] forcats_0.5.0             stringr_1.4.0            
#>  [7] dplyr_0.8.5               purrr_0.3.4              
#>  [9] readr_1.3.1               tidyr_1.1.0              
#> [11] ggplot2_3.3.2.9000        tidyverse_1.3.0          
#> [13] lubridate_1.7.4           visreg_2.7.0             
#> [15] tibble_3.0.1              riskRegression_2020.02.05
#> [17] prodlim_2019.11.13        flexsurv_1.1.1           
#> [19] survival_3.1-8            pracma_2.2.9             
#> [21] magrittr_1.5              kableExtra_1.1.0         
#> [23] glmnet_4.0-2              Matrix_1.2-18            
#> [25] data.table_1.12.8         cowplot_1.0.0            
#> [27] colorspace_1.4-1          casebase_0.9.0           
#> 
#> loaded via a namespace (and not attached):
#>  [1] TH.data_1.0-10      VGAM_1.1-3          ellipsis_0.3.1     
#>  [4] ggstance_0.3.3      htmlTable_1.13.3    base64enc_0.1-3    
#>  [7] fs_1.3.2            rstudioapi_0.11     farver_2.0.3       
#> [10] MatrixModels_0.4-1  fansi_0.4.1         mvtnorm_1.0-12     
#> [13] xml2_1.3.0          codetools_0.2-16    knitr_1.29         
#> [16] Formula_1.2-3       jsonlite_1.7.0      cluster_2.1.0      
#> [19] dbplyr_1.4.2        png_0.1-7           compiler_3.6.2     
#> [22] httr_1.4.1          backports_1.1.8     assertthat_0.2.1   
#> [25] cli_2.0.2           acepack_1.4.1       htmltools_0.5.0    
#> [28] quantreg_5.54       tools_3.6.2         gtable_0.3.0       
#> [31] Rcpp_1.0.4.6        cellranger_1.1.0    vctrs_0.3.1        
#> [34] nlme_3.1-143        iterators_1.0.12    xfun_0.15          
#> [37] rvest_0.3.5         lifecycle_0.2.0     polspline_1.1.17   
#> [40] muhaz_1.2.6.1       MASS_7.3-51.5       zoo_1.8-7          
#> [43] scales_1.1.1        hms_0.5.3           sandwich_2.5-1     
#> [46] SparseM_1.78        RColorBrewer_1.1-2  rticles_0.13       
#> [49] yaml_2.2.1          gridExtra_2.3       rms_5.1-4          
#> [52] rpart_4.1-15        latticeExtra_0.6-29 stringi_1.4.6      
#> [55] foreach_1.5.0       checkmate_2.0.0     lava_1.6.6         
#> [58] shape_1.4.4         rlang_0.4.6         pkgconfig_2.0.3    
#> [61] evaluate_0.14       lattice_0.20-38     labeling_0.3       
#> [64] htmlwidgets_1.5.1   cmprsk_2.2-9        tidyselect_1.1.0   
#> [67] deSolve_1.27.1      plyr_1.8.6          R6_2.4.1           
#> [70] generics_0.0.2      Hmisc_4.3-1         multcomp_1.4-12    
#> [73] DBI_1.1.0           withr_2.2.0         pillar_1.4.4       
#> [76] haven_2.3.1         foreign_0.8-74      mgcv_1.8-31        
#> [79] nnet_7.3-12         mstate_0.2.12       modelr_0.1.5       
#> [82] crayon_1.3.4        rmarkdown_2.3       jpeg_0.1-8.1       
#> [85] grid_3.6.2          readxl_1.3.1        reprex_0.3.0       
#> [88] digest_0.6.25       webshot_0.5.2       numDeriv_2016.8-1.1
#> [91] stats4_3.6.2        munsell_0.5.0       viridisLite_0.3.0  
#> [94] quadprog_1.5-8
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> Local:    write-popTime /home/sahir/git_repositories/cbpaper
#> Remote:   write-popTime @ origin (https://github.com/sahirbhatnagar/cbpaper.git)
#> Head:     [dad6070] 2020-07-18: cleaned cs1
\end{CodeOutput}
\end{CodeChunk}
